DraftFunctions

### 2021-09-30 R/DraftFunctions.Rmd
Vignette
Doc corrections

usethis::use_data(SpeciesCriteria)
```

@@

if (any(duplicated(Paracou6_2016)==TRUE))
  stop ("Tree identifiers (idTree) are not unique.") # stop function if the tree identifiers (idTree) are not unique
if (all(Paracou6_2016$Plot==Paracou6_2016$Plot[1])==FALSE) #all the Plot values are equal?
  stop ("Your inventory concerns different plots (Plot). Our function simulates logging at the plot level.") 
# Remove out-plot trees (A faire)

>>>>

usethis::use_data(SpeciesCriteria)
```
```{r}
ScenariosTable <- read_csv("D:/VSC Kourou/DATA/ScenariosTable.csv", 
    col_types = cols(Winching = col_factor(levels = c("0", 
        "1", "2")), DirectionalFelling = col_factor(levels = c("0", 
        "1", "2"))), trim_ws = TRUE)

usethis::use_data(ScenariosTable)
```

@@

if (any(duplicated(Paracou6_2016)==TRUE))
  stop ("Tree identifiers (idTree) are not unique.") # stop function if the tree identifiers (idTree) are not unique
if (all(Paracou6_2016$Plot==Paracou6_2016$Plot[1])==FALSE) #all the Plot values are equal?
  stop ("Input inventory concerns different plots (Plot). Our function simulates logging at the plot level.") 
# Remove out-plot trees (A faire)
